\documentclass[10pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{tabularx}

\setlength{\parindent}{0pt}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

{\LARGE \textbf{EURO BAE}}\\
\vspace{2pt}
Senior Backend Engineer Candidate \\
\vspace{4pt}
Dublin, Ireland \quad | \quad Fluent in English and Korean

\section*{Professional Summary}
Backend-focused software engineer with strong experience in Python-based systems, cloud-native backend development, and distributed architectures. Proven ability to design, build, and optimize scalable services using AWS, PostgreSQL, Docker, and CI/CD pipelines. Demonstrated technical leadership through industry-academic partnerships, FinTech-style trading systems, and sustainability-driven infrastructure optimization. Experienced in mentoring, cross-functional collaboration, and delivering production-grade backend solutions.

\section*{Technical Skills}
\begin{tabularx}{\textwidth}{lX}
Languages: & Python, Java, JavaScript/TypeScript, C, R \\
Backend \& Architecture: & Backend Development, Microservices Architecture, Distributed Systems, REST APIs, GraphQL \\
Cloud \& DevOps: & AWS, Docker, CI/CD Pipelines, Linux, Git, Cloudflare, Grafana \\
Databases: & PostgreSQL, MySQL, MongoDB, Oracle \\
Frontend (Supporting): & React, React Native, Next.js \\
Security \& Testing: & OWASP ZAP, Zest \\
\end{tabularx}

\section*{Professional Experience}

\textbf{Undergraduate Demonstrator} \hfill Trinity College Dublin, Dublin \\
\textit{September 2025 -- Present}
\begin{itemize}[leftmargin=*]
  \item Mentored and supported students in backend-oriented coursework using Python, data processing workflows, and web technologies.
  \item Reinforced best practices in debugging, system design thinking, and collaborative software development.
\end{itemize}

\textbf{Full Stack Engineer Intern (Industry--Academic Partnership)} \hfill Workday, Dublin \\
\textit{January 2025 -- April 2025}
\begin{itemize}[leftmargin=*]
  \item Designed and implemented backend services using Node.js and REST APIs, contributing to over 80\% of the project codebase.
  \item Established a full CI/CD pipeline by configuring GitLab Runner on a Raspberry Pi with secure SSH tunneling, improving deployment reliability.
  \item Migrated database and application services to energy-efficient infrastructure, reducing power consumption by approximately 93\%, aligning with sustainable cloud computing principles.
  \item Collaborated with senior engineers on system design, code reviews, and deployment strategies in a distributed team environment.
\end{itemize}

\textbf{Software Engineer Trainee} \hfill Samsung SDS, Suwon \\
\textit{February 2024 -- July 2024}
\begin{itemize}[leftmargin=*]
  \item Automated enterprise workflows using RPA tools, improving operational efficiency in demonstration environments.
  \item Prototyped a smart factory system integrating backend services, machine learning components, and IoT data pipelines.
  \item Gained exposure to event-driven system concepts and enterprise-scale backend solutions.
\end{itemize}

\textbf{Data Analyst Intern} \hfill Media \& Data Institute, Seoul \\
\textit{May 2021 -- September 2021}
\begin{itemize}[leftmargin=*]
  \item Refactored backend data access from SQL-based queries to GraphQL APIs, improving flexibility and frontend integration.
  \item Worked on data governance and privacy practices aligned with ethical data collection and compliance requirements.
\end{itemize}

\section*{Selected Projects}

\textbf{A.T.M. (Automated Trading Manager) -- FinTech}
\begin{itemize}[leftmargin=*]
  \item Built a Python-based automated trading system integrating the Binance API to execute trades based on technical indicators and market conditions.
  \item Implemented risk management features including stop-loss, entry logic, and transaction fee analysis.
  \item Simulated trading strategies to evaluate performance, reflecting real-world FinTech and payments system constraints.
\end{itemize}

\textbf{AURA (AI-Based Work Efficiency Enhancer)}
\begin{itemize}[leftmargin=*]
  \item Led a 5-member team to develop a backend-driven productivity analytics platform integrating Azure Face API and language models.
  \item Designed data pipelines to process real-time user interaction data and generate actionable insights.
  \item Conducted code reviews and oversaw deployment to ensure system reliability and scalability.
\end{itemize}

\textbf{OLY (Community-Driven Expat Platform)}
\begin{itemize}[leftmargin=*]
  \item Led a 7-member development team, providing technical leadership, task planning, and version control governance.
  \item Developed backend services supporting authentication, marketplace transactions, rentals, currency exchange, and real-time chat.
  \item Deployed mobile applications to TestFlight and Google Play internal testing using cloud-based backend infrastructure.
\end{itemize}

\section*{Education}

\textbf{Trinity College Dublin} \hfill Dublin \\
Honors Bachelor’s in Integrated Computer Science \hfill \textit{September 2021 -- May 2027}
\begin{itemize}[leftmargin=*]
  \item Global Excellence Undergraduate Scholarship; Trinity International Foundation Scholarship.
  \item Software Engineering Project Industry Award (Sustainability); Huawei Tech Arena 2025 LLM Hackathon (3rd Prize).
  \item Relevant coursework: Software Engineering Project, Algorithms and Data Structures, Concurrent Systems, Computer Architecture, Statistical Analysis.
\end{itemize}

\section*{Honors \& Certifications}
\begin{itemize}[leftmargin=*]
  \item Global Excellence Undergraduate Scholarship -- Trinity International Foundation.
  \item Software Engineering Project Industry Award (Sustainability).
  \item Huawei Tech Arena 2025 LLM Hackathon -- 3rd Prize.
\end{itemize}

\end{document}